Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/paper.tex
restructure discussion of multiphase

With $14$ free parameters our first concern is discovering which are
the parameters that can be safeley constrained by \tol's line shape.

From the K-S tests we confirm that only 3 parameters 
can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
All the other parameters cannot be constrained from \tol's
observations.

The best models are shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep. I don't think you can get larger errors
  with the available date. By simple inspection of Figure 2 we can
  see that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have there is a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile represents
the kinematics of the clumps, that is, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ \& $\beta_{\rm cl}$. 
Furthermore, the relatively low mean number of clumps per line of
sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion
of the clumps implies the  existence of low-density inter-clump 
regions where \lya photons can freely propagate which leads to an
emergent spectrum close to the intrinsic one as well as to the high
flux at line center as observed. 
Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

>>>>

With $14$ free parameters our first concern is discovering which 
parameters matter the most.
From the K-S tests we find that only 3 parameters 
are confidently constrained by \tol's line shape;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).

This illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$.  
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile follows 
the clump kinematics. In other words, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.. 
Furthermore, the relatively low mean number of clumps per line of
sight, $f_{\mathrm{cl}}$, combined with the high velocity dispersion
of the clumps implies existence of low-density inter-clump 
regions where \lya photons can freely propagate.
This gives result to an emergent spectrum close to the intrinsic one, explaining the high
flux at line center as observed.

Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.
